Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

\medskip
Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain. %\red{For example, during water flooding, efficiency is related with capillary number. The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES ! HOW THIS NEW SENTENCE IS RELATED TO THE PREVIOUS -- 'Flow instabilities ... of the domain' ... AND HOW IS IT RELATED WITH THE FOLLOWING SENTENCES?)}. 
When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.

>>>>

Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain. %\red{For example, during water flooding, efficiency is related with capillary number. The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES ! HOW THIS NEW SENTENCE IS RELATED TO THE PREVIOUS -- 'Flow instabilities ... of the domain' ... AND HOW IS IT RELATED WITH THE FOLLOWING SENTENCES?)}. 
When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
